How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-15 tse-paper/content.tex
small changes to introduction (more ideas but wanna know Moritz' plans), start on update lit survey

To gain an impression on how researchers are using information from
build logs within their research to support
developers, we conducted a systematic mapping study.
Our goal was to classify how, and what for, researchers use build logs as
a source of data (\textbf{RQ1}).

@@

\Cref{fig:overview} gives an overview of our research steps.

\begin{simplebox}{Research Questions}
\begin{itemize}
  \item[\textbf{RQ1:}] Which build log analysis techniques exist?
  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk
  retrieval technique for build logs?
\end{itemize}
\end{simplebox}

@@

The results of our empirical comparison study on the chunk retrieval
techniques
show that the structural representation of the targeted chunk greatly
influences
the performance of the chunk retrieval techinques.
\Cref{lst:chunk-example} shows two exemplary
log chunks from Android build logs marked in blue.
Both chunks contain the information on why the
corresponding build failed.
When PBE is trained with these two examples it produces
a regular expression program similar to the one presented in
\Cref{lst:prose-program-simplified}.
The retrieval
starts after a colon and a line separator and before a capital
letter.
It ends before two line separators, consistent with the two example
chunks from \Cref{lst:chunk-example}.
This shows, that the characters structuring the text around the chunk are
cruicial for regular expressions to identify a log chunk.
In fact, if the third example from \Cref{lst:chunk-example-3} with a
different structural representation is added to the training set,
PBE is not able to syntesize a program and returns
``\texttt{no program found}''.
We express this difference in structural representation through
dividing log chunks into structural categories.
The chunks from \Cref{lst:chunk-example}
are in the \emph{same structural category}, while the chunk from
\Cref{lst:chunk-example-3} is in a \emph{different structural category}.

@@

% TODO (Caro): Integrate Petersen's guidelines
The field of analyzing build
logs is relatively young; we know there have been scattered
research efforts on build log analysis, mostly where the
log analysis was a side-part of the article.
To the best of our
knowledge, there has not been an attempt to systematically overview
and survey approaches for processing build logs.

@@

@@

The first goal in analyzing system log files is ubiquitously to
separate constant and variable parts within a log
message~\cite{nagappan2010abstracting,he2017towards}.
Next, the log
messages are clustered into log events, unifying messages with
identical constant parts and varying parameters.
The output of a log
parser is an ordered list of timed events and their corresponding
parameter values~\cite{he2016evaluation}.
This structured log is then
the input to various machine learning and data mining processes.
%Researchers mine patterns for operational
%profiling~\cite{nagappan2009efficiently},
%debugging~\cite{oliner2012advances}, performance analytics or anomaly
%detection~\cite{nagappan2010abstracting}.
% Xu et
%al.~\cite{xu2009detecting} leverage the connection of log statements
%to the source code producing them to separate messages into constant
%and variable parts more accurately.

The techniques developed for system log analysis can also be applied
to build logs.
One example is comparing execution traces to reference
traces of intended behavior to detect anomalies.
Amar et
al.~\cite{amar2019mining} employed a similar approach to detect
relevant lines in build logs.
%Classic log parsers interpret the whole log file into a sequence of
%events.
% A similar approach could also be applied to build logs to
%determine the sequence of executed build steps or phases.
In this article, we focus on extracting a single specified information
from the build log as a whole with chunk retrieval techniques.
Chunk
retrieval techniques are used as a part of log parsing to retrieve the
values of variable parts in a log message, e.g.\ by using regular
expressions~\cite{nagappan2010abstracting,xu2009detecting}.

>>>>

% TODO: 4 sentence description of the steps in graphic?
\Cref{fig:overview} gives an overview of our research steps.
We conducted a systematic mapping study,
to gain an impression on how researchers are using information from
build logs within their research or to support
developers.
% We implemented three promising techniques that retrieve
% chunks of text from build logs and can be adapted to
% a specific project and use case by giving examples of build logs and
% correpsonding chunks.
% We evaluated the
Our goal was to clarify the state-of-research on build log
analysis (\textbf{RQ1}).

@@

\begin{simplebox}[minipage boxed title*=-5cm]{Research Questions}
\begin{itemize}
  \item[\textbf{RQ1:}] What is the state-of-research on build
  log analysis?
  \item[\textbf{RQ2:}] When are PBE, CTS or KWS suited to
  retrieve chunks from build logs?
\end{itemize}
\end{simplebox}

% TODO: move down to where mentioned in detail
% \begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
% {\textbf{RQ1:} What is the state-of-research on build
% log analysis?}
% \begin{itemize}
%   \item[\textbf{RQ1.1:}] Which information is targeted?
%   \item[\textbf{RQ1.2:}] Which techniques are used?
%   \item[\textbf{RQ1.3:}] Which build logs are analyzed?
% \end{itemize}
% \end{simplebox}

% \begin{simplebox}[minipage boxed title*=-2.5cm,
% attach boxed title to top center={yshift=-6mm}]
% {\textbf{RQ2:} When are PBE{,} CTS or KWS suited to
% retrieve chunks from build logs?}
% \begin{itemize}
%   \item[\textbf{RQ2.1:}] How many examples does a technique need to
%   perform best?
%   \item[\textbf{RQ2.2:}] How structurally similar do the examples
%   need for a technique to be applicable?
%   \item[\textbf{RQ2.3:}] How accurate are the retrievals of a technique?
% \end{itemize}
% \end{simplebox}

@@

% TODO: this could move to the chunk retrieval techniques section
The results of our empirical comparison study on the chunk retrieval
techniques
show that the structural representation of the targeted chunk greatly
influences
the performance of the chunk retrieval techinques.
\Cref{lst:chunk-example} shows two exemplary
log chunks from Android build logs marked in blue.
Both chunks contain the information on why the
corresponding build failed.
When PBE is trained with these two examples it produces
a regular expression program similar to the one presented in
\Cref{lst:prose-program-simplified}.
The retrieval
starts after a colon and a line separator and before a capital
letter.
It ends before two line separators, consistent with the two example
chunks from \Cref{lst:chunk-example}.
This shows, that the characters structuring the text around the chunk are
cruicial for regular expressions to identify a log chunk.
In fact, if the third example from \Cref{lst:chunk-example-3} with a
different structural representation is added to the training set,
PBE is not able to syntesize a program and returns
``\texttt{no program found}''.
We express this difference in structural representation through
dividing log chunks into structural categories.
The chunks from \Cref{lst:chunk-example}
are in the \emph{same structural category}, while the chunk from
\Cref{lst:chunk-example-3} is in a \emph{different structural category}.

@@

The field of analyzing build
logs is relatively young; We have seen scattered
research efforts on build log analysis.
However,the processing of build logs was often
a side-part of the article.
To the best of our
knowledge, there has not been an attempt to systematically overview
and survey approaches for processing build logs.
We conducted a systematic mapping study to determine the
state-of-research on build log analysis following the guidelines
by Petersen et al.~\cite{petersen2015guidelines}.

In the following section, we explain how build log analysis differs
from system log analysis.

@@

The first goal in analyzing system log files is ubiquitously to
separate constant and variable parts within a log
message~\cite{nagappan2010abstracting,he2017towards}.
Next, the log
messages are clustered into log events, unifying messages with
identical constant parts and varying parameters.
The output of a log
parser is an ordered list of timed events and their corresponding
parameter values~\cite{he2016evaluation}.
This structured log is then
the input to various machine learning and data mining processes.

The techniques developed for system log analysis can also be applied
to build logs.
One example is comparing execution traces to reference
traces of intended behavior to detect anomalies.
Amar et
al.~\cite{amar2019mining} employed a similar approach to detect
relevant lines in build logs.
In this article, we focus on extracting a single specified information
from the build log as a whole with chunk retrieval techniques.
Chunk
retrieval techniques are used as a part of log parsing to retrieve the
values of variable parts in a log message, e.g.\ by using regular
expressions~\cite{nagappan2010abstracting,xu2009detecting}.

@@

### 2020-04-15 tse-paper/paper.tex
small changes to introduction (more ideas but wanna know Moritz' plans), start on update lit survey

\usepackage[most]{tcolorbox}
\newtcolorbox{simplebox}[2][]{enhanced,
    minipage boxed title,
    sharp corners,
    colback=white,
    colbacktitle=white,
    coltitle=black,
    boxrule=1pt,
    left=8mm,
    right=8mm,
    bottom=2mm,
    top=4mm,
    boxed title style={colframe=white},
    attach boxed title to top center={yshift=-3mm,yshifttext=-1mm},
    title=#2,#1}

>>>>

\usepackage[most]{tcolorbox}
\newtcolorbox{simplebox}[2][]{enhanced,
    minipage boxed title*,
    sharp corners,
    colback=white,
    colbacktitle=white,
    coltitle=black,
    boxrule=1pt,
    left=8mm,
    right=8mm,
    bottom=2mm,
    top=4mm,
    boxed title style={colframe=white},
    attach boxed title to top center={yshift=-3mm},
    center title,
    title=#2,#1}
